---
title: "FX_MODEL"
author: "Paritosh Kalla"
date: "7/19/2019"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
```{r}
rm(list = ls())
```

Importing the Dataset

```{r}
df = read.csv('Sample_Data.csv')
keeps = c('Product','Status','CCY.Pair','CCY.Amount') # Can also be done using select() from dplyr package
df = df[keeps]
```

Filtering the dataset for "FXFWD" and "INOPICS"

```{r}
library(tidyverse)
fxfwd = df %>% filter(Product == 'FXFWD') %>% filter(Status == 'INOPICS')
```

```{r}
fxfwd = fxfwd %>% group_by(CCY.Pair) %>% summarise(CCY.Amount = sum(CCY.Amount))
```

Removing the column names 

```{r}
colnames(fxfwd) = NULL
```

Transposing the columns

```{r}
fxfwd = data.frame(t(fxfwd))
colnames(fxfwd) <- as.character(unlist(fxfwd[1,]))
fxfwd = fxfwd[-c(1),]
```

Creating a empty dataframe

```{r}
fxfwd_sim = data.frame(matrix("", ncol = 10, nrow = 499))
colnames(fxfwd_sim) = names(fxfwd)
```

Generating simulated data for each currency pair

Data Simulation for AUD/USD with white noise
```{r}
fxfwd_sim$`AUD/USD` = c(arima.sim(model = list(order = c(0,0,0)), n = 499) + 13825.68)
plot(fxfwd_sim$`AUD/USD`, type = 'l')
```

Data Simulation for EUR/CAD with MA component
```{r}
fxfwd_sim$`EUR/CAD` = c(arima.sim(model = list(ma = 0.2488, order = c(0,0,1)), n = 499) + 58000)
plot(fxfwd_sim$`EUR/CAD`, type = 'l')
```

Data Simulation for EUR/GBP with AR(2) component
```{r}
fxfwd_sim$`EUR/GBP` = c(arima.sim(model = list(ar = c(0.8897, -0.4858), order = c(2,0,0)), n = 499) + 109924.22)
plot(fxfwd_sim$`EUR/GBP`, type = 'l')
```

Data Simulation for EUR/USD with MA(2) component
```{r}
fxfwd_sim$`EUR/USD` = c(arima.sim(model = list(ma = c(-0.2279, 0.2488), order = c(0,0,2)), n = 499) + 2750328)
plot(fxfwd_sim$`EUR/USD`, type = 'l')
```

Data Simulation for GBP/CAD with both AR and MA component
```{r}
fxfwd_sim$`GBP/CAD` = c(arima.sim(model = list(ar = 0.8, ma = 0.2488, order = c(1,0,1)), n = 499) + 6000)
plot(fxfwd_sim$`GBP/CAD`, type = 'l')
```

Data Simulation for GBP/USD with Non Linear Series
```{r}
set.seed(12121212)
  n=499 
  u<-rnorm(n) 
  x<-rep(0,n) 
  for(i in 2:n){ 
  x[i] <- x[i-1] + u[i]
  } 
fxfwd_sim$`GBP/USD` = x + 296105.85
plot(fxfwd_sim$`GBP/USD`, type = 'l')
plot(diff(fxfwd_sim$`GBP/USD`), type = 'l')
```

Data Simulation for USD/CAD with Heterogenous Variance (SARIMA)
```{r}
library(smooth)
ourSimulation = sim.ssarima(orders=list(ar=c(5,10),i=c(0,2),ma=c(0,5)), lags=c(1,7), obs=499, iprob=0.2)
fxfwd_sim$`USD/CAD` = ourSimulation$data + 2695816.66
plot(fxfwd_sim$`USD/CAD`, type = 'l')
```

Data Simulation for USD/JPY with Simple Exponential Smoothing 
```{r}
ourSimulation <- sim.es("ANN", frequency=12, obs=499)
fxfwd_sim$`USD/JPY` = ourSimulation$data + 6000000
plot(fxfwd_sim$`USD/JPY`, type = 'l')
```

Data Simulation for USD/MXN with Complex Exponenetial Smoothing
```{r}
ourSimulation <- sim.ces(frequency=10, obs=499, nsim=1)
fxfwd_sim$`USD/MXN` = ourSimulation$data + 3813
plot(fxfwd_sim$`USD/MXN`, type = 'l')
```

Data Simulation for USD/NOK with SARIMA
```{r}
library(smooth)
ourSimulation <-sim.ssarima(orders=list(ar=c(0,5),i=c(0,2),ma=c(0,1)), lags=c(1,12), constant=TRUE, obs=499)
fxfwd_sim$`USD/NOK` = ourSimulation$data + 1707579.20
plot(fxfwd_sim$`USD/NOK`, type = 'l')
```


Combining the simulated dataframe with actual dataframe
```{r}
#install.packages("plyr")
library(plyr)
fxfwd = rbind.fill(fxfwd,fxfwd_sim)
```

Adding the item column 
```{r}
#rownames(fxfwd) = seq(as.Date("2012/1/1"), by = "day", length.out = 500)
fxfwd$item = seq(1:nrow(fxfwd))
```

Checking the structure of the dataframe
```{r}
str(fxfwd)
```

Changing the structure to numeric
```{r}
fxfwd[] <- lapply(fxfwd, function(x) as.numeric(as.character(x)))
```

Plots for Checking Stationarity, p and q values

```{r}
library(car)
attach(fxfwd)
par(mfrow = c(2,2), mai = c(0.7, 0.3, 0.3, 0.3))
loop.vector = 1:10
for (i in names(fxfwd[1:10])){
plot(item, fxfwd[,i], pch = 19, type = 'l',main = colnames(fxfwd[i]), ylab = "Amount", xlab = "Frequency")
  hist(fxfwd[,i], main = colnames(fxfwd[i]), xlab = "Amount")
  acf(fxfwd[,i])
  pacf(fxfwd[,i])
}
```

PP Test for Checking Stationarity

```{r}
for(i in names(fxfwd[1:10])){
  print(colnames(fxfwd[i]))
print(PP.test(fxfwd[,i]))
}
```

```{r}
library(urca)
jotest=ca.jo(fxfwd, type="trace", K=2, ecdet="none", spec="longrun")
summary(jotest)
```

Splitting into Training Set and Test Set

```{r}
#install.packages("caTools")
library(caTools)
split = sample.split(fxfwd, SplitRatio = 2/3)
train = subset(fxfwd, split == TRUE)
test = subset(fxfwd, split == FALSE)
```

ARIMA Model for each Currency Pair

ARIMA for AUD/USD with p = 2, q = 2, d = 0
```{r}
maudusd = arima(train$`AUD/USD`, order = c(2,0,2))
faudusd = predict(maudusd, n.ahead = length(test$`AUD/USD`))
test$`AUD/USD` - faudusd$pred
n <- length(test$`AUD/USD` - faudusd$pred)
RMSE1 <- sqrt(sum((test$`AUD/USD` - faudusd$pred)^2)/n)
RMSE1
ts.plot(test$`AUD/USD`, faudusd$pred, lty = c(1,3))
```


ARIMA for EUR/CAD with p = 5, q = 2, d = 0
```{r}
meurcad = arima(train$`EUR/CAD`, order = c(5,0,2))
feurcad = predict(meurcad, n.ahead = length(test$`EUR/CAD`))
test$`EUR/CAD` - feurcad$pred
n <- length(test$`EUR/CAD` - feurcad$pred)
RMSE2 <- sqrt(sum((test$`EUR/CAD` - feurcad$pred)^2)/n)
RMSE2 
ts.plot(test$`EUR/CAD`, feurcad$pred, lty = c(1,3))
```

ARIMA for EUR/GBP with p = 4, q = 2, d = 0
```{r}
meurgbp = arima(train$`EUR/GBP`, order = c(4,0,2))
feurgbp = predict(meurgbp, n.ahead = length(test$`EUR/GBP`))
test$`EUR/GBP` - feurgbp$pred
n <- length(test$`EUR/GBP` - feurgbp$pred)
RMSE3 <- sqrt(sum((test$`EUR/GBP` - feurgbp$pred)^2)/n)
RMSE3 
ts.plot(test$`EUR/GBP`, feurgbp$pred, lty = c(1,3))
```

ARIMA for EUR/USD with p = 2, q = 2, d = 0
```{r}
meurusd = arima(train$`EUR/USD`, order = c(2,0,2))
feurusd = predict(meurusd, n.ahead = length(test$`EUR/USD`))
test$`EUR/USD` - feurusd$pred
n <- length(test$`EUR/USD` - feurusd$pred)
RMSE4 <- sqrt(sum((test$`EUR/USD` - feurusd$pred)^2)/n)
RMSE4 
ts.plot(test$`EUR/USD`, feurusd$pred, lty = c(1,3))
```

ARIMA for GBP/CAD with p = 0, q = 2, d = 0
```{r}
mgbpcad = arima(train$`GBP/CAD`, order = c(0,0,2))
fgbpcad = predict(mgbpcad, n.ahead = length(test$`GBP/CAD`))
test$`GBP/CAD` - fgbpcad$pred
n <- length(test$`GBP/CAD` - fgbpcad$pred)
RMSE5 <- sqrt(sum((test$`GBP/CAD` - fgbpcad$pred)^2)/n)
RMSE5 
ts.plot(test$`GBP/CAD`, fgbpcad$pred, lty = c(1,3))
```

ARIMA for GBP/USD with p = 0, q = 3, d = 1
```{r}
mgbpusd = arima(train$`GBP/USD`, order = c(0,1,3))
fgbpusd = predict(mgbpusd, n.ahead = length(test$`GBP/USD`))
test$`GBP/USD` - fgbpusd$pred
n <- length(test$`GBP/USD` - fgbpusd$pred)
RMSE6 <- sqrt(sum((test$`GBP/USD` - fgbpusd$pred)^2)/n)
RMSE6
ts.plot(test$`GBP/USD`, fgbpusd$pred, lty = c(1,3))
```

ARIMA for USD/CAD with p = 2, q = 2, d = 0
```{r}
musdcad = arima(train$`USD/CAD`, order = c(2,0,2))
fusdcad = predict(musdcad, n.ahead = length(test$`USD/CAD`))
test$`USD/CAD` - fusdcad$pred
n <- length(test$`USD/CAD` - fusdcad$pred)
RMSE7 <- sqrt(sum((test$`USD/CAD` - fusdcad$pred)^2)/n)
RMSE7 
ts.plot(test$`USD/CAD`, fusdcad$pred, lty = c(1,3))
```

ARIMA for USD/JPY with p = 0, q = 14, d = 0
```{r}
musdjpy = arima(train$`USD/JPY`, order = c(0,0,14))
fusdjpy = predict(musdjpy, n.ahead = length(test$`USD/JPY`))
test$`USD/JPY` - fusdjpy$pred
n <- length(test$`USD/JPY` - fusdjpy$pred)
RMSE8 <- sqrt(sum((test$`USD/JPY` - fusdjpy$pred)^2)/n)
RMSE8 
ts.plot(test$`USD/JPY`, fusdjpy$pred, lty = c(1,3))
```

ARIMA for USD/MXN with p = 0, q = 6, d = 0
```{r}
musdmxn = arima(train$`USD/MXN`, order = c(0,0,6))
fusdmxn = predict(musdmxn, n.ahead = length(test$`USD/MXN`))
test$`USD/MXN` - fusdmxn$pred
n <- length(test$`USD/MXN` - fusdmxn$pred)
RMSE9 <- sqrt(sum((test$`USD/MXN` - fusdmxn$pred)^2)/n)
RMSE9 
ts.plot(test$`USD/MXN`, fusdmxn$pred, lty = c(1,3))
```

ARIMA for USD/NOK with p = 0, q = 8, d = 0
```{r}
musdnok = arima(train$`USD/NOK`, order = c(0,0,8))
fusdnok = predict(musdnok, n.ahead = length(test$`USD/NOK`))
test$`USD/NOK` - fusdnok$pred
n <- length(test$`USD/NOK` - fusdnok$pred)
RMSE10 <- sqrt(sum((test$`USD/NOK` - fusdnok$pred)^2)/n)
RMSE10 
ts.plot(test$`USD/NOK`, fusdnok$pred, lty = c(1,3))
```

